Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-12 MS/ms.Rmd
Modified MS a bit becasue of dependency in box. Fixed up a bunch of box stuff to be consistent with main MS a little more, mainly just add sigma to denote variances, just some added equation for readers to hopefully make it a littkle more clear the equivalency for Delta Methods.

Meta-analysis is a tool that provides comparative physiologists with powerful, unbiased and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies. Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species. Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges. Despite this ambition, research designs in comparative physiology can appear, at the outset, as being vastly different to each other (e.g., using different temperatures or treatment dosages). Differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges". Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-regression models to both account for factors driving differences across studies and make them more comparable. In addition, we formalise effect size measures that provide comparative physiologists with a means to directly make effect measures comparable, removing 'nuisance heterogeneity' without the need to resort to more complex statistical models that may be harder to interpret. We also describe more general approaches that can be usefully applied to a variety of different contexts to derive 'new' effects sizes and sampling variances. The effect sizes and their corresponding sampling variances we describe should help physiologists deal with common treatment differences across studies. By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.

@@

Generally, contributors to effect size heterogeneity fall within a number of broad categories. First, sampling variance contributes to heterogeneity; the variability driven by the inherent uncertainty in sampling a given population. We cannot sample the entire population and nor do we necessarily want to. As a consequence, we need to rely on a sub-sample to estimate a population parameter (e.g., correlation between two traits). How many independent samples we collect impacts our precision in estimating this 'true' effect [@Borenstein2019]. In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly because it is known -- hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013]. Second, there are sociological factors impacting heterogeneity. These include attitudes towards publishing non-significant results. Low powered studies that do not find an 'effect' or that find an effect in the opposite direction often lead to what is called publication bias [@Jennions2013; @Nakagawa2021b; @Rothstein2005]. Third, there is real biology driving differences in effects. This is particularly true in comparative physiology where different species with varying habitats, life-histories, mating systems and reproductive modes are synthesised. As comparative physiologists, this is the stuff that gets us up every morning! Much variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy. We can model these biological factors to test predictions from hypotheses that we believe are key players impacting mean effect size and direction. This improves our understanding of the biological world around us and helps inform on future research directions. Finally, methodological factors are also big contributors to effect variability. In some cases, these methodological factors are of direct interest. For example, the methods for measuring an outcome variable can result in different effects, and it is important we know and understand this as it can determine how experiments are designed in the future. In other cases, methodological factors might be considered 'nuisance heterogeneity' [following from @Cooperetal2019] -- factors we know vary, but are rather unsurprising to us. These might include differences in temperature, pH, dosages, water potential etc. It might already be clear that these factors will have an impact on the magnitude of an effect, but they might distract from the core interest of a meta-analysis. In some cases, however, the latter factors might actually not be 'nuisance' variables but the main interest of a synthesis. However, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.

@@

Before embarking on "meta-analytic enlightenment" it is worth first understanding how comparative physiologists are currently conducting meta-analyses / comparative analysis.  As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists. To better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled we conducted a literature survey. To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species. We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis? 2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies (i.e., 'nuisance heterogeneity')? 3) If so, was the variation accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis? We collected additional

@@

As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nuisance heterogeneity'. For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment. Even modelling just the mean often needs to control for various sources of 'nuisance heterogeneity'. For example, standard metabolic rate (SMR) is temperature dependent. As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest in of itself). While we could of course model this explicitly, this may not always be desirable. It can often be useful to standardise the effect to both ease its interpretation and simplify modelling. In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself. We highlight two examples in the box focusing mainly on generality. Below, we show using a common, well understood effect measure of interest to comparative physiology, $Q_{10}$ how we can formalise a traditional effect sizes', such as $lnRR$, to capture this 'nuisance variation'.

@@

Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018] we might extract data from studies manipulating corticosterone in bird eggs. Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species. If the studies are experimental in nature than a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable. We then might fit an overall multilevel meta-analytic model as follows: 
$$
\begin{equation} 
Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\
(\#eq:MLMM)
\end{equation} 
$$ $$
\begin{equation} 
a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}),\
sp_{k[i]}\sim N(0, \sigma^{2}_{species}\textbf{I}),\
s_{j[i]}\sim N(0, \sigma^{2}_{study}\textbf{I}),\
e_{i}\sim N(0, \sigma^{2}_{residual}\textbf{I}),\
m_{i} \sim N(0, v_{i})\
(\#eq:dist)
\end{equation} 
$$

where $Y_{i}$ is the *i*th effect size (*i* = 1 ... $N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect (a random effect) for species *k* applied to effect size *i*. Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}\textbf{A})$], where $\textbf{A}$ is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect. This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is weighted by the inverse sampling variance of each effect size. The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012]. This is formalised in what we call 'heterogeneity analysis' which we describe below. Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticosterone have on reproduction relative to control conditions? <!--- don't we need to mention in the case of VCV for mi--->

Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatment. The most we can say about it, is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies. In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.

@@

We can, however, apply some simple transformations to make the overall mean estimate more intuitive to understand with the added benefit that it can help improve the interpretation of non-linear parameters estimated by the model [@Schielzeth2010; @GelmanHill2007]. One simple transformation would be to centre the variable $x_{j}$, by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage). The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$ in the meta-regression model. When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups. Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude (e.g., when the dosage different in 10 uL /g). This approach can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done and the overall mean adjusted to include the new variable, in additional to dosage. Of course, if one is not interested in the magnitude of effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models). Here, one can model the mean for each group (i.e., control and treatment group), and account for the known sampling variance associated with each group mean. Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output changes. It is important to recognise that all means need to be comparable and that these models are more complex to fit. While they can be equivalent to 'contrast-based' models, they require complex interactions to be estimated [@Nakagawa2015].

@@

where *k* is the number of studies and the weights, $w_{i} = \frac{1}{v_{i}}$, can be calculated as the inverse of the sampling variance ($v_{i}$) for each effect size, *i*.

@@

Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010]. If we want to formally assess how much effect size variation is the result of 'methodological factors 'nuisance' variation, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.

@@

Heterogeneity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019]. Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorporate measures of dispersion around a mean effect size providing information about the likely effect size one can expect if we were to randomly sample a new population. For example, assume that we were interested in the overall impact of salinity stress in freshwater fish. To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (~15-20ppm Na Cl) compared to freshwater (~0ppm Na Cl) controls; using SMD to quantify the magnitude of effect salinity had on swim performance. We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85. The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population. In addition, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c]. This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c]. As such, we encourage more meta-analysts to report these.

>>>>

Meta-analysis is a tool that provides comparative physiologists with powerful, unbiased and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies. Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species. Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges. Despite this ambition, research designs in comparative physiology can appear, at the outset, as being vastly different to each other (e.g., using different temperatures or treatment dosages). Differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges". Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-regression models to both account for factors driving differences across studies and make them more comparable. In addition, we formalise effect size measures that provide comparative physiologists with a means to directly make effect measures comparable, removing 'nuisance heterogeneity' without the need to resort to more complex statistical models that may be harder to interpret. We also describe more general approaches that can be usefully applied to a variety of different contexts to derive 'new' effects sizes and sampling variances. The effect sizes and their corresponding sampling variances that we describe should help physiologists deal with common treatment differences across studies. By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.

@@

Generally, contributors to effect size heterogeneity fall within a number of broad categories. First, sampling variance contributes to heterogeneity; the variability driven by the inherent uncertainty in sampling a given population. We cannot sample the entire population and nor do we necessarily want to. As a consequence, we need to rely on a sub-sample to estimate a population parameter (e.g., correlation between two traits). How many independent samples we collect impacts our precision in estimating this 'true' effect [@Borenstein2019]. In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly because it is known -- hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013]. Second, there are sociological factors impacting heterogeneity. These include attitudes towards publishing non-significant results. Low powered studies that do not find an 'effect' or that find an effect in the opposite direction often lead to what is called publication bias [@Jennions2013; @Nakagawa2021b; @Rothstein2005]. Third, there is real biology driving differences in effects. This is particularly true in comparative physiology where different species with varying habitats, life-histories, mating systems and reproductive modes are synthesised. As comparative physiologists, this is the stuff that gets us up every morning! Much variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy. We can model these biological factors to test predictions from hypotheses that we believe are key players impacting mean effect size and direction. This improves our understanding of the biological world around us and helps inform on future research directions. Finally, methodological factors are also big contributors to effect variability. In some cases, these methodological factors are of direct interest. For example, the methods for measuring an outcome variable can result in different effects, and it is important we know and understand this as it can determine how experiments are designed in the future. In other cases, methodological factors might be considered 'nuisance heterogeneity' [following from @Cooperetal2019] -- factors we know vary, but are rather unsurprising to us. These might include differences in temperature, pH, dosages, water potential etc. It might already be clear that these factors will have an impact on the magnitude of an effect, but they might distract from the core interest of a meta-analysis. In some cases, however, the latter factors might actually not be 'nuisance' variables but the main interest of a synthesis. Regardless, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.

@@

Before embarking on "meta-analytic enlightenment" it is worth first understanding how comparative physiologists are currently conducting meta-analyses / comparative analysis.  As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists. To better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled we conducted a literature survey. To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species. We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis? 2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies (i.e., 'nuisance heterogeneity')? 3) If so, was the variation accounted for in the effect size or during analysis? and finally, 4) how many analyses used 'weighted' meta-analytic models?

@@

As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nuisance heterogeneity'. For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment. Even modelling just the mean often needs to control for various sources of 'nuisance heterogeneity'. For example, standard metabolic rate (SMR) is temperature dependent. As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest in of itself). While we could of course model this explicitly, this may not always be desirable. It can often be useful to standardise the effect to both ease its interpretation and simplify modelling. In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself. We highlight two examples in the box focusing mainly on generality. Below, we show using a common, well understood effect measure of interest to comparative physiologists, $Q_{10}$, how we can formalise a traditional effect size, such as $lnRR$, to capture this 'nuisance variation'.

@@

Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018]. We might extract data from studies manipulating corticosterone in bird eggs. Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species. If the studies are experimental in nature than a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable. We then might fit an overall multilevel meta-analytic model as follows: 
$$
Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\ \\
a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}), \\
sp_{k[i]}\sim N(0, \sigma^{2}_{species}\textbf{I}), \\
s_{j[i]}\sim N(0, \sigma^{2}_{study}\textbf{I}), \\
e_{i}\sim N(0, \sigma^{2}_{residual}\textbf{I}), \\
m_{i} \sim N(0, v_{i}\textbf{I}) \\
$$

where $Y_{i}$ is the *i*th effect size (*i* = 1 ... $N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect (a random effect) for species *k* applied to effect size *i* [i.e., species effects because of shared evolutionary history, @Cinar2021]. Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}\textbf{A})$], where $\textbf{A}$ is a phylogenetic correlation matrix derived from a phylogenetic tree. $sp_{k[i]}$ is an additional species-specific effect for the *k*th species applied to effect size *i* [i.e., these are species-specific effects because of shared ecology and other factors, @Cinar2021], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect. This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is weighted by the inverse sampling variance of each effect size. Importantly, if we have effect sizes that are derived from the *same* sample of animals (or plants) (e.g., may be because many traits are measured on the same sets of animals) then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying \textbf{I} to include off-diagonals that account for this covariance [See Box 1 and @Noble2017]. The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012]. This is formalised in what we call 'heterogeneity analysis' which we describe below. Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticosterone have on reproduction relative to control conditions?

Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatments used in the sample of studies. The most we can say about it, is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies. In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.

@@

We can, however, apply some simple transformations to make the overall mean estimate more intuitive to understand with the added benefit that it can help improve the interpretation of non-linear parameters estimated by the model [@Schielzeth2010; @GelmanHill2007]. One simple transformation would be to centre the variable $x_{j}$, by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage). The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$ in the meta-regression model. When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups. Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude (e.g., when the dosage difference is 10 uL /g).  Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses this centering can be particularly useful in making these means more interpretable.Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted can be interpreted in the context of this new variable in additional to dosage. Of course, if one is not interested in the magnitude of effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models). Here, one can model the mean for each group (i.e., control and treatment group), and account for the known sampling variance associated with each group mean. Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output changes. It is important to recognise that all means need to be comparable and that these models are more complex to fit. While they can be equivalent to 'contrast-based' models, they require complex interactions to be estimated [@Nakagawa2015].

@@

where *k* is the number of studies and the weights, $w_{i} = \frac{1}{v_{i}}$, can be calculated using the inverse of the sampling variance ($v_{i}$) for each effect size, *i*.

@@

Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010]. If we want to formally assess how much effect size variation is the result of 'nuisance' variation, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.

@@

Heterogeneity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019]. Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorporate measures of dispersion around a mean effect size providing information about the likely effect size one can expect if we were to randomly sample a new population. For example, assume that we were interested in the overall impact of salinity stress in freshwater fish. To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (~15-20ppm Na Cl) compared to freshwater (~0ppm Na Cl) controls; using SMD to quantify the magnitude of effect salinity had on swim performance. We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85. The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population. In addition, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c]. This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these.
